The Structure of Human Language Reflects Limitations of Working Memory

### 2019-04-22 paper-short.tex
figure

- example? something like `John threw the trash out'
- something with a relative clause `The child that was playing on the street had a red ball' -- should not forget the `child'.
- center embedding: `The physician who consulted the cardiologist checked the files in her office' -- (Fedorenko, Gibson, and Rohde (2006))

>>>>

- discontinuous idioms
- example? something like `John threw the trash out'
- particle verb, with completely idiomatic meaning. `give up' `the climber gave the attempt to reach the peak of Mount Everest up' could have figure `he gave the attempt to sculpture out of marble up'. understanding what the word means in contet requires understanding of the past.
- 
- something with a relative clause `The child that was playing on the street had a red ball' -- should not forget the `child'.
- center embedding: `The physician who consulted the cardiologist checked the files in her office' -- (Fedorenko, Gibson, and Rohde (2006))
